MSAD_PCA_Walkthrough

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Added the knitr chunk for downloading the package. I had it commented out previously.

This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter. The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component. This package can be downloaded from GitHub by running the following:
%   <<r packLoad_GitHub, eval = FALSE>>=
%   devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
% @
\noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

>>>>

This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter. The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the statistical process monitoring component. This package can be downloaded from GitHub by running the following:
<<r packLoad_GitHub, eval = FALSE>>=
 devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
@
\noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Added the knitr chunk for downloading the package. I had it commented out previously.

This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter. The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component. This package can be downloaded from GitHub by running the following:
%   <<r packLoad_GitHub, eval = FALSE>>=
%   devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
% @
\noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

@@

##   Data: num [1:4142, 1:5] 0.2109 0.0632 0.4924 0.7234 0.6277 ...

@@

##   Data: num [1:4141, 1:7] 2 3 1 1 1 1 1 1 1 1 ...

@@

##  $ Alarms         :An 'xts' object on 2015-05-19 13:13:00/2015-05-19 13:13:00 containing:
##   Data: num [1, 1:11] 1.81 -2.32 4.2 2.07 -2.11 ...
##   ..$ : chr [1:11] "x" "y" "z" "x.1" ...

@@

##   .. ..$ SPE_threshold   : Named num 4.71

@@

##   .. ..$ T2_threshold    : Named num 60.5

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.423 -0.382 0.437 0.431 -0.315 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.205 0 0 1.579
##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.6 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.14

@@

##   .. ..$ T2_threshold    : Named num 76.8

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.496 -0.065 0.49 -0.523 -0.183 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.735 ...
##   .. ..$ muTrain         : Named num [1:6] 2.979 -0.564 -4.508 2.952 -0.589 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 7.2

@@

##   .. ..$ T2_threshold    : Named num 82.7

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.451 -0.455 0.16 -0.464 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.494
##   .. ..$ muTrain         : Named num [1:6] 0.528 0.27 1.423 0.569 0.256 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.9 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.6844440 -1.565320 1.1324768 0.3534816
## 2015-05-22 07:01:00     1 0.5454614 -1.369986 0.9184724 0.6844440
## 2015-05-22 07:02:00     1 0.6468377 -1.593779 0.8900444 0.5454614
## 2015-05-22 07:03:00     1 0.3543316 -1.361402 0.7855688 0.6468377
## 2015-05-22 07:04:00     1 0.3831960 -1.455579 0.6319864 0.3543316
## 2015-05-22 07:05:00     1 0.5734844 -1.406738 0.9210589 0.3831960
##                             y.1       z.1
## 2015-05-22 07:00:00  0.08705337 0.4466149
## 2015-05-22 07:01:00 -1.56532037 1.1324768
## 2015-05-22 07:02:00 -1.36998580 0.9184724
## 2015-05-22 07:03:00 -1.59377911 0.8900444
## 2015-05-22 07:04:00 -1.36140249 0.7855688
## 2015-05-22 07:05:00 -1.45557880 0.6319864
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1         y.1
## 2015-05-22 07:00:00 0.6844440 -1.565320 1.1324768 0.3534816  0.08705337
## 2015-05-22 07:01:00 0.5454614 -1.369986 0.9184724 0.6844440 -1.56532037
## 2015-05-22 07:02:00 0.6468377 -1.593779 0.8900444 0.5454614 -1.36998580
## 2015-05-22 07:03:00 0.3543316 -1.361402 0.7855688 0.6468377 -1.59377911
## 2015-05-22 07:04:00 0.3831960 -1.455579 0.6319864 0.3543316 -1.36140249
## 2015-05-22 07:05:00 0.5734844 -1.406738 0.9210589 0.3831960 -1.45557880
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.4466149 0.2948716        0 28.028452       0    NA
## 2015-05-22 07:01:00 1.1324768 0.9816014        0  5.025385       0    NA
## 2015-05-22 07:02:00 0.9184724 0.0316290        0  4.773963       0    NA
## 2015-05-22 07:03:00 0.8900444 0.8505646        0  6.333569       0    NA
## 2015-05-22 07:04:00 0.7855688 0.2234181        0  6.613971       0    NA
## 2015-05-22 07:05:00 0.6319864 0.4523686        0  5.922610       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter. The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the statistical process monitoring component. This package can be downloaded from GitHub by running the following:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
 \hlstd{devtools}\hlopt{::}\hlkwd{install_github}\hlstd{(}\hlstr{"gabrielodom/mvMonitoring"}\hlstd{,} \hlkwc{auth_token} \hlstd{=} \hlstr{"tokenHere"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}
\noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

@@

##   Data: num [1:4142, 1:5] 0.042 0.492 1.208 1.139 0.742 ...

@@

##   Data: num [1:4142, 1:7] 2 3 1 1 1 1 1 1 1 1 ...

@@

##  $ Alarms         :An 'xts' object of zero-width

@@

##   .. ..$ SPE_threshold   : Named num 4.39

@@

##   .. ..$ T2_threshold    : Named num 61.4

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.381 0.437 0.432 -0.313 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.565
##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.97 1.37 -2.05 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.79

@@

##   .. ..$ T2_threshold    : Named num 76.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4944 -0.0882 0.4873 -0.5234 -0.1921 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.727 ...
##   .. ..$ muTrain         : Named num [1:6] 3.019 -0.561 -4.533 2.991 -0.586 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 5.58

@@

##   .. ..$ T2_threshold    : Named num 80.1

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.394 0.448 0.452 -0.167 0.464 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.277 0 0 0.498
##   .. ..$ muTrain         : Named num [1:6] 0.528 0.273 1.441 0.57 0.259 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.2 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.6516822 -1.487152 0.8868843 0.3772442
## 2015-05-22 07:01:00     1 0.6959653 -1.524802 0.7687056 0.6516822
## 2015-05-22 07:02:00     1 0.4693409 -1.202725 0.7970705 0.6959653
## 2015-05-22 07:03:00     1 0.5744935 -1.239971 0.6663379 0.4693409
## 2015-05-22 07:04:00     1 0.5872442 -1.238700 0.8654388 0.5744935
## 2015-05-22 07:05:00     1 0.6820071 -1.452199 0.9107379 0.5872442
##                            y.1       z.1
## 2015-05-22 07:00:00  0.1208201 0.5190793
## 2015-05-22 07:01:00 -1.4871516 0.8868843
## 2015-05-22 07:02:00 -1.5248019 0.7687056
## 2015-05-22 07:03:00 -1.2027252 0.7970705
## 2015-05-22 07:04:00 -1.2399706 0.6663379
## 2015-05-22 07:05:00 -1.2386996 0.8654388
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1        y.1
## 2015-05-22 07:00:00 0.6516822 -1.487152 0.8868843 0.3772442  0.1208201
## 2015-05-22 07:01:00 0.6959653 -1.524802 0.7687056 0.6516822 -1.4871516
## 2015-05-22 07:02:00 0.4693409 -1.202725 0.7970705 0.6959653 -1.5248019
## 2015-05-22 07:03:00 0.5744935 -1.239971 0.6663379 0.4693409 -1.2027252
## 2015-05-22 07:04:00 0.5872442 -1.238700 0.8654388 0.5744935 -1.2399706
## 2015-05-22 07:05:00 0.6820071 -1.452199 0.9107379 0.5872442 -1.2386996
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.5190793 0.5746873        0 28.479963       0    NA
## 2015-05-22 07:01:00 0.8868843 0.3065558        0  4.594196       0    NA
## 2015-05-22 07:02:00 0.7687056 2.2496108        0  6.313058       0    NA
## 2015-05-22 07:03:00 0.7970705 1.4836139        0  7.071992       0    NA
## 2015-05-22 07:04:00 0.6663379 1.6703320        0  6.605812       0    NA
## 2015-05-22 07:05:00 0.8654388 0.4398132        0  5.638591       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}
